---
title: "Lab 2 Homework"
author: "Netra Patel"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: spacelab
    toc: no
---

## Instructions
Answer the following questions and complete the exercises in RMarkdown. Please embed all of your code and push your final work to your repository. Your final lab report should be organized, clean, and run free from errors. Remember, you must remove the `#` for the included code chunks to run. Be sure to add your name to the author header above.  

Make sure to use the formatting conventions of RMarkdown to make your report neat and clean!  

1. What is a vector in R?  
ANS: A vector is type of data structure which stores the values of the data matrix. 

2. What is a data matrix in R?  
ANS: It is a sequence that organizes data or objects into rows and columns. 

3. Below are data collected by three scientists (Jill, Steve, Susan in order) measuring temperatures of eight hot springs. Run this code chunk to create the vectors.  
```{r}
spring_1 <- c(36.25, 35.40, 35.30)
spring_2 <- c(35.15, 35.35, 33.35)
spring_3 <- c(30.70, 29.65, 29.20)
spring_4 <- c(39.70, 40.05, 38.65)
spring_5 <- c(31.85, 31.40, 29.30)
spring_6 <- c(30.20, 30.65, 29.75)
spring_7 <- c(32.90, 32.50, 32.80)
spring_8 <- c(36.80, 36.45, 33.15)
```

4. Build a data matrix that has the springs as rows and the columns as scientists.  
```{r}
spring_command <- c(spring_1,spring_2,spring_3,spring_4,spring_5,spring_6,spring_7,spring_8)
spring_command

spring_matrix <- matrix(spring_command, nrow = 8, byrow = T)
spring_matrix

springs <- c("1","2","3","4","5","6","7","8")

scientists <- c("Jill", "Steve", "Susan")

rownames(spring_matrix) <- springs
colnames(spring_matrix) <- scientists

spring_matrix
```